Verifying Demonstrations

### 2017-08-27 conclusions.tex
Edits conclusions

  \begin{question}
    This is similar to the double-spending problem for cryptocurrencies, can 
    we reuse any such techniques?
    (Not like in Bitcoin, but more like ecash~\cite{ecash} and the like.)
  \end{question}
\end{frame}

\begin{frame}
  \frametitle{Distributed systems}
  \begin{question}
    \begin{itemize}
      \item Malicious nodes want to provide Alice with a view that her proof is 
        included.
      \item Everyone else is provided a view without Alice.
      \item How can we ensure a consistent view for everyone?
    \end{itemize}
  \end{question}

  \begin{question}
    How can we do blockchain branch and merge?
    That is needed to recover from the above attack.
  \end{question}
\end{frame}

@@

>>>>

  \begin{question}
    Can we achieve receipt freeness and protect from Sybil?
  \end{question}
\end{frame}

@@

\begin{frame}
  \frametitle{Blockchains, distributed systems}
  \begin{question}
    \begin{itemize}
      \item Malicious nodes want to provide Alice with a view that her proof is 
        included.
      \item Everyone else is provided a view without Alice.
      \item How can we ensure a consistent view for everyone?
    \end{itemize}
  \end{question}

  \begin{question}
    Can we do blockchain branch and merge?
  \end{question}
\end{frame}
